---
title       : Comparison of KNN, CART and Random Forests classification methods
subtitle    : (clscompare application)
author      : Chau Nguyen (nhchau@gmail.com) - Aug 20, 2015
job         : UET, VNU
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
url         :
    libraries: ../libraries
    assets: ../assets
---

## Introduction
- clscompare is an application uses to compare KNN, CART and Random Forests classification methods.
Application URL: https://nhchau.shinyapps.io/clscompare. Data set: iris

<center>
```{r, echo=F, result="hide", fig.width=4.5, fig.height=4.5}
library(caret)
library(rpart)
set.seed(12345)
iris$Species = relevel(iris$Species, "versicolor")
iris$Species = relevel(iris$Species, "virginica")
plot(iris[,1:4], col=iris$Species, main="The iris data set")
```
</center>
- Method of comparison: Apply the above classification methods on the same training and testing data sets
then compare prediction results

--- .intro #1

## The iris data set
- The followings are the iris data set structure and the first four items:
```{r,echo=F}
str(iris)
head(iris, 4)
```
- Predictors: Sepal.Length Sepal.Width Petal.Length Petal.Width, outcome: Species

---

## Application input parameters
- A seed number for random number generation
- Relative size of the training data set with reference to the iris data set
- Classfication method to use

--- 

## Application outputs
- Plots: Classification results (left) and Species (right) of the test data set.

```{r, echo=F, result="hide", fig.width=6, fig.height=3.5}
index=createDataPartition(iris$Species, p=0.6, list=F)
te = iris[-index,]
tr = iris[index, ]
fit = train(Species~., method="rpart", data=tr)
ClassifiedResult = predict(fit, te)
par(mfrow=c(1,2))
# Plot classification result
ggplot(te, aes(x=Petal.Width, y=Petal.Length, color=ClassifiedResult))+
	geom_point(size=3)+stat_density2d()
# Plot Species data
ggplot(te, aes(x=Petal.Width, y=Petal.Length, color=Species))+
	geom_point(size=3)+stat_density2d()
```
- The confusion matrix
- The iris data set in details: List of all items in data sets. Each item
has an additional indicator specifying the item belonging to training or testing data sets
- The test data set with an additional score on each item specifying whether the item
is correctly/incorrectly classified
